Very simplified likelihood

### 2024-03-19 inst/very_simplified_likelihood.Rmd
work on lane advantage in olympic athletics

>>>>

# Athletics

```{r loadolymp}
O <- read.table("olympic_athletics_mens_100m.txt",header=TRUE)
head(O)
```

```{r analuyzelmp,cache=TRUE}
jjf <- function(x){f_vec_arn(x,O$rank,O$n,log=TRUE)}
system.time(optolym <- optimize(jjf, c(0.45,0.5), maximum=TRUE))
```

```{r}
optolym
jjf(0.5)
jjf(optolym$maximum)
(LR <- 2*(jjf(optolym$maximum)-jjf(0.5)))
pchisq(LR,df=1,lower.tail=FALSE)
```

```{r makeolymplike}
a <- seq(from=0.3,to=0.65,len=45)
L <- f_vec_arn(a,O$rank,O$n,log=TRUE)
Lmax <- jjf(optolym$maximum)
Lmax
L <- L-Lmax
```

```{r findcredint}
(a_lower <- uniroot(function(x){jjf(x)+2-Lmax},interval=c(0.3,0.5))$root)
(a_upper <- uniroot(function(x){jjf(x)+2-Lmax},interval=c(0.5,0.6))$root)
```

```{r plotolymp}
plot(a,L,type='l',ylab="log-likelihood",lwd=2)
abline(h=c(0,-2))
ahat <- optolym$maximum
segments(x0=ahat,y0=-1.5,y1=0)
text(ahat,-0.91,expression(hat(a)==0.573),pos=2)
abline(v=0.5,lty=3)

segments(x0=a_lower,y0=-1.5,y1=-3.5)
segments(x0=a_upper,y0=-1.5,y1=-3.5)

text(x=a_lower,y=-3,"0.380",pos=4)
text(x=a_upper,y=-3,"0.563",pos=2)
```
